Escape Analysis and Specialization in a Tracing JIT

### 2010-09-28 talk/pepm2011/paper.tex
add two paragraphs about virtualizables, I guess they are cuttable

XXX virtualizables, store sinking

>>>>

\subsection{Virtualizables}
\label{sub:Virtualizables}

\cfbolz{probably can be cut in case of space problems}

One problem to the successful application of the allocation removal techniques
described in the previous sections is the presence of frame-introspection
features in many dynamic languages. Languages such as Python and Smalltalk allow
the programmer to get access to the frames object that the interpreter uses to
store local variables. This is a useful feature, as makes the implementation of
a debugger possible in Python without needing much support from the VM level. On
the other hand, it severely hinders the effectiveness of allocation removal,
because every time an object is stored into a local variable, it is stored into
the frame-object, which makes it escape.

This problem is solved by making it possible to the interpreter author to add
some hints into the source code to declare instances of one class as frame
objects. The JIT will then fill these objects only lazily when they are actually
accessed (\eg because a debugger is used). Therefore in the common case, nothing
is stored into the frame objects, making the problem of too much escaping go
away. This is a common approach in VM implementations \cite{XXX}, the only
novelty in our approach lays in its generality, because most other JITs are just
specifically written for one particular language.

% subsection Virtualizables (end)
XXX store sinking
